Topological Equivariant Artist Model for Visualization Library Architecture

### 2021-10-07 paper/main.tex
sheafs

We encode individual datasets in the fiberbundle as sections, and we follow the convention that $\Gamma(U_i, \dtotal)$ denotes the set of sections $\{\dsection^{j}:U_i \rightarrow \dfiber_{U_{i}}\}_{j\in I}$ of the fiber bundle \dtotal\ over an open set $\U_{i}$.  The sections $\Gamma(\dbase, \dtotal)$ are called the global sections of $\dtotal$ \cite{SheafMathematics2021,spanier1989algebraic}. Each section is how we represent a unique dataset, where the set of sections $\Gamma$ is the set of all datasets that have the same data fields in the \dfiber\ and continuity as encoded in\dbase\. For example, Spivak describes tables that have the same schema and discrete index as sections of the same fiber bundle\cite{spivakSIMPLICIALDATABASES}.

\begin{definition} The category $\mathcal{\dtotal}$ consists of 
  \begin{itemize}
    \item\textit{object} the functor $\sheaf: \mathcal{K}^{op} \rightarrow \Gamma(\mathcal{K}, \dtotal)$, which is a sheaf\cite{spanier1989algebraic,SheafMathematics2021,nlab:presheaf} \note{this might need an appendix/footnote: it is a presheaf b/c $\iota:\Gamma(U_2)\rightarrow \Gamma(U_1)$ and $\iota: \dbase_1\rightarrow \dbase_2$ (smaller subspace in bigger subspace, larger section includes smaller), which means $\mathcal{K}$ is contravariant, and $\Gamma(U_{i}, \dtotal)$ is \textbf{set}}
    \item \textit{morphisms} the endomorphic\cite{fongInvitationAppliedCategory2019} maps $\cdot: \dtotal\rightarrow \dtotal$, which are the fiber maps $\monoid:\mathcal{\dfiber}\rightarrow \mathcal{\dfiber}$ when the morphisms are restricted to a single point in the base space $\dbasepoint\in \dbase$
  \end{itemize}
\end{definition}

@@

\begin{equation}
  \begin{tikzcd}
    \mathcal{\dtotal} \arrow[r, "\vartist"] \arrow[d, "M"] & \mathcal{\gtotal} \arrow[d, "A(M)"] \arrow[d, "\ca"] \\
    \mathcal{\dtotal} \arrow[r, "\vartist"]                & \mathcal{\gtotal}                                
  \end{tikzcd}
\end{equation}

>>>>

We encode individual datasets in the fiberbundle as sections, and we follow the convention that $\Gamma(U_i, \dtotal)$ denotes the set of sections $\{\dsection^{j}:U_i \rightarrow \dfiber_{U_{i}}\}_{j\in I}$ of the fiber bundle \dtotal\ over an open set $\U_{i}$.  As mentioned in \autoref{sec:related-work:fiber-bundles}, the fiber space is embedded in the total space $\dfiber \hookrightarrow \dtotal$. The sections $\Gamma(\dbase, \dtotal)$ are called the global sections of $\dtotal$ \cite{SheafMathematics2021,spanier1989algebraic}. Each section is how we represent a unique dataset, where the set of sections $\Gamma$ is the set of all datasets that have the same data fields in the \dfiber\ and continuity as encoded in\dbase\. For example, Spivak describes tables that have the same schema and discrete index as sections of the same fiber bundle\cite{spivakSIMPLICIALDATABASES}.

\begin{definition} The category $\mathcal{\dtotal}$ consists of 
  \begin{itemize}
    \item\textit{object} the contravariant functor $\sheaf: \mathcal{K}^{op} \rightarrow \Gamma(\mathcal{K}, \dtotal)$
    \item \textit{morphisms} the endomorphic\cite{fongInvitationAppliedCategory2019} maps $\cdot: \dtotal\rightarrow \dtotal$, which are the fiber maps $\monoid:\mathcal{\dfiber}\rightarrow \mathcal{\dfiber}$ when the morphisms are restricted to a single point in the base space $\dbasepoint\in \dbase$
  \end{itemize}
\end{definition}

The functor object of $\mathcal{E}$ is a presheaf because the definition of a presheaf is that it is a contravariant functor from a category $\mathcal{K}$ to a set \cite{spanier1989algebraic,SheafMathematics2021,nlab:presheaf}. As illustrated in the diagram, 
\begin{equation}
  \label{eq:artist:[presheaf}
  \begin{tikzcd}[row sep=small]
    U_1 \arrow[dd, "\iota"'] & {\Gamma(U_1, \dtotal)}                              \\
    {} \arrow[r, "\sheaf"]   & {}                                                  \\
    U_2                      & {\Gamma(U_2, \dtotal)} \arrow[uu, "\iota^*"']
    \end{tikzcd}
\end{equation}
the functor \sheaf\ is contravariant because the inclusion map $\iota$ between objects in $\mathcal{K}$ goes the in the opposite direction from the map $\iota$ between open set objects in $\mathcal{K}$ \cite{riehlCategoryTheoryContext}. The open set $U_1$ is a subset of $U_2$, therefore $\iota: U_1 \rightarrow U_2$. On the other hand, a set of functions defined on a space $U_2$ must be defined on the subspace $\iota: \Gamma(U_2, \dbase) \rightarrow \Gamma(U_1, \dbase)$ but the reverse does not need to be true. For example, a continuous function defined over the interval $\left[.25,.5\right]$ need not be defined over $\left[0, 1\right]$ but must exist over  $\left[.3, .45\right]$. We use the notation $\mathcal{K}^{op}$ to signify that the functor $\sheaf$ is contravariant and $\sheaf$ to denote that it is a sheaf. A sheaf is a presheaf where sections are defined over unions of open sets \cite{nlab:sheaf,ghristElementaryAppliedTopology2014}

@@

\begin{equation}
  \label{eq:artist:natural-transform}
  \begin{tikzcd}
  \mathcal{\dtotal} \arrow[r, "\vartist"] \arrow[d, "\monoid"'] & \mathcal{\gtotal} \arrow[d, "\vartist(\monoid)"] \\
  \mathcal{\dtotal} \arrow[r, "\vartist"]                       & \mathcal{\gtotal}                               
  \end{tikzcd}
\end{equation}
